A Technique for Inter-Catalogue Recommendations

### 2014-06-10 paper2/paper.tex
Added Data section and re-worked part of Experiment section.

\section*{Introduction}
Recommender systems have become a critical component for online retailers in
nearly every space of retail. Whether the products are movies or clothes or research
articles, large retailer tend to have a way of recommending products based on
other previously viewed or purchased products.

These recomendations usually come from a combination of content-based
information and collaborative filtering techniques. The content-based approach
uses information about the products, such as category or descriptioin, to
connect related products. Alone, however, this approach is usually unable to
capture the subtle ways products may actually be related. Collaborative
filtering, on the other hand, learns relations from aggregated user behavior. 
Such recommendation often have explicit ttiles like ``People who liked 
this product also liked these products''. Collaborative filtering has proven to
be effective at recommending products, given that there is a large amount of user 
data.

@@

\section*{Experiment}
To measure the success of constructing recommendations, we design the following
experiment:

First, we scrape all of the clothing products from Macy's website at 
www.macys.com. For each product we save its image, what category of clothing it
is in, its description, and a list of other products recommended for it.

Next, we partition all of the Macy's products into two disjoint sets to simulate 
the catalogues of two different retailers. To make this partition realistic, 
we ensure that no brand has products in both catalogue. We remove all 
recommendations between products from one partition to the other, thus creating 
two entirely disjoint and unconnected catalogues.

>>>>

\section*{Introduction}
Recommender systems have become a critical component for online retailers in
nearly every space of retail. Whether the products are movies or clothes or
research articles, large retailers tend to have a way of recommending products
based on others previously viewed or purchased products.

These recomendations usually come from a combination of content-based
information and collaborative filtering techniques. The content-based approach
uses information about the products, such as category or description, to connect
related products. Alone, however, this approach is usually unable to capture the
subtle ways products may actually be related. Collaborative filtering, on the
other hand, learns relations from aggregated user behavior.  Such
recommendations often have explicit titles like ``People who liked this product
also liked these products''. Collaborative filtering has proven to be effective
at recommending products, given that there is a large amount of user data.

@@

\section*{Data}
For this work, we utilize most of the product catalog of Macy's as presented at
www.macys.com. This catalog consists of numerous categories of mostly apparel,
each of which includes hundreds to thousands of items. We confine this study to
the 49 categories within the two main parent categories ``Men'' and ``Women''
that contain at least 200 items that are associated to multiple brands. In
total, this dataset consists of 66,071 items in 49 categories with some items
listed in multiple categories. For each item we record its description, all
categories within which it is listed, and its associated recommendations. By
{\em recommendations}, we are referring to the items---there are typically four
in the case of Macy's---that are displayed on a product's details page under the
heading ``Customers Also Shopped''. The presence of these recommendations
implicitly forms a directed graph over the product catalogue, in which the nodes
are the {\em products} or {\em items} and the edges are the {\em
recommendations}. These graphs play a central role in this study.

\section*{Experiments}
Our goal is to develop methods for connecting initially disconnected
recommendation graphs. That is, given two online retailers, each with a website
that displays items in their respective catalogue, where each item is
accompanied by several {\em recommended} items, we are presented with two
disconnected recommendation graphs. We would like to associate ``good''
recommendations for items in one catalogue with items in the other catalogue. In
this way, we are effectively introducing edges that connect the two
recommendation graphs. Formulating this inter-retailer recommendations problem
in terms of graphs offers insight in how to evaluate our recommendation choices
as well as how to choose ``good'' recommendations. Leveraging the graph
structure for evaluation is discussed in this section while exploiting the graph
for the purpose of making better recommendations is addressed in a subsequent
section.

To evaluate our inter-retailer recommendation methods, we simulate the problem
by randomly partitioning Macy's products into two disjoint sets. Given the
original recommendation graph, each partition therefore corresponds to a graph
cut. Our premise is that an ideal recommendation method could guess the edges in
this cut with high precision and recall.

Precision, recall, and $F_1$ score are well-known metrics for evaluating
prediction algorithms.  Together, these metrics capture how effective one is at
guessing the items within a target set. Consider a typical Macy's category, for
example, Dresses, which contains about $3,500$ items. Randomly partitioning
results in two sets, each with about $1,750$ items. For each interset
recommendation, we must therefore choose two nodes, one from each of the two
sets. That is, we have $1,750 \times 1,750 > 3 \times 10^6$ choices. Choosing
the correct edges is a formidable challenge to say the least. It is therefore
worth asking: Are some prediction errors better or worse than others? The graph
nature of our problem reveals that the answer is yes. It is better to guess an
edge that connects two items that are separated by two edges in the original
graph than to connect two items that are separated by five edges. We therefore
introduce the notion of {\em 2-precision}, {\em 2-recall}, and {\em 2-}$F_1$ are
defined as

\begin{align}
\text{\em 2-precision} &= \left|\left\{(u,v) \in P | d_L(u,v) \leq 2
\right\}\right|
\\\text{\em 2-recall} &= \left|\left\{(u,v) \in L | d_P(u,v) \leq 2
\right\}\right|
\\\text{\em 2-}F_1 &= 2\cdot \frac{\text{\em 2-precision} \cdot \text{\em
2-recall}}{\text{\em 2-precision} + \text{\em 2-recall}}
\end{align}
where $P$ is the set of predicted edges, $L$ is the set of lost edges (i.e.
those in the cut resulting from the partition), and $d_L(u,v)$ is the distance
between nodes $u$ and $v$ in the original unpartitioned graph, and $d_P(u,v)$ is
the distance between nodes $u$ and $v$ in the new graph formed using the
predicted edges in $P$.

In these experiments, we perform the partitioning on a per-category basis.

Next, for each category (e.g. Women Activewear, Men Dress Shirts, etc.), we
partition the products into two disjoint sets to simulate the catalogues of two
distinct retailers. Importantly, we ensure that the items of each brand are
entirely within a single partition. In this way, we preclude the easiest method
of associating two items: recongnizing a common brand. This is done to increase
the difficulty and realism of our experiment.

To make this partition realistic, we
ensure that no brand has products in both catalogue. We remove all
recommendations between products from one partition to the other, thus creating
two entirely disjoint and unconnected catalogues.
